% !TEX root = C:/Users/piyus/knowledge/Project_Specific_Knowledge/public/fm_radio/stages/power/power.tex
\documentclass[12pt, letterpaper]{article}

\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {C:/Users/piyus/knowledge/Project_Specific_Knowledge/public/fm_radio/stages/power/pictures} }

\title{Power Notes}
\author{Piyush Sud}
\date{9/30/2024}
\begin{document}
\maketitle

\pagebreak

\section{High Level Design}

\begin{itemize}
    \item The entire system will be powered by a single 14V power supply. This is quite noisy, so we will need LDOs for all the logic level supplies. For the 14V power supply, let's use this: \url{https://www.amazon.com/Universal-Adapter-Charger-Interchangeable-Adapters/dp/B0CPPPVG1G/ref=sr_1_3?crid=2KLES6HGGUCI2&dib=eyJ2IjoiMSJ9.4r7Cki0zlXUtJQKT-1hYuwlbBar_RD_jqO8kzk3YThAURSIVDYEFQyR5ftYOVwzLVe2k_Az4fdqSYnsUkUqUPjn3C6fEPJ39Uh68V2AjiPOvsE10gY9pYzNfYLFxlHjSZ6pAs_0IBiFielAX_ZnYKr8bwzX3uQVFOwX4dY91pt86CmygiIaYbwo5iViyVy0eNgYn-7KdniKJ8pnflphrXGPhvf6tuvrXRrycFjWWcVM.ct3hYxPMlpg8BKUBbNV4c0ou_J1ZHIAdPAI9vWayJgM&dib_tag=se&keywords=dc+power+supply+14V&qid=1727954337&sprefix=dc+power+supply+14v%2Caps%2C368&sr=8-3}
    \item Let's use the AZ1117ID-ADJTRG1 for our 12V supply. It has a good PSRR of 70 dB @ 120 Hz. This works since Vin = Vout + 2V for the adj supply.
    \item Let's use the AZ1117ID-3.3 and AZ1117ID-5 for our 3.3V and 5V supplies respectively. For those, \(1.5V < Vin - Vout < 10V\), so we can use the 12V supply as Vin so that Vin - Vout = 8.7V for the 3V3 supply and 7V for the 5V supply. 
    \item Let's use the recommended 10 uF and 22 uF decoupling caps as recommended in the datasheet, and select caps that are low ESR.
\end{itemize}

\section{Calculations}

\begin{itemize}
    \item For the adjustable supply, the resistors needed are given by this formula: VOUT=VREF * (1+R2/R1) + IADJ * R2
    \item The reference voltage is fixed at 1.25V. The IADJ can be ignored since it's very small.
    \item To get a 12V supply from 14V and setting R2 = 2kohms, 1k/R1 = 12/1.25 - 1 so R1 = 232.558139534 ohms.
\end{itemize}

\end{document}